Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population

### 2022-09-26 src/tex/results.tex
cleanup captions

\begin{figure*}[ht!]
    \script{mass_distribution_plot.py}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/mass_distribution_plot.pdf}
        \caption{Plot showing the primary mass distribution inferred with the \textsc{MSpline} model with 40 knots for $m_1$. We show the results for the 
        \textsc{PowerlawSpline} (blue) model from the LVK's GWTC-3 population analyses.}
        \label{fig:mass_distribution}
    \end{centering}
\end{figure*}

@@

\begin{figure}
    \script{plot_iid_spinmag.py}
    \includegraphics[width=0.45\textwidth]{figures/iid_spinmag.pdf}
    \caption{Caption.}
    \label{fig:iid_spinmag_dist}
\end{figure}

@@

\begin{figure}
    \script{plot_ind_spinmag.py}
    \includegraphics[width=0.45\textwidth]{figures/ind_spinmag.pdf}
    \caption{Caption.}
    \label{fig:ind_spinmag_dist}
\end{figure}

@@

\begin{figure}
    \script{plot_iid_spintilt.py}
    \includegraphics[width=0.45\textwidth]{figures/iid_spintilt.pdf}
    \caption{Caption.}
    \label{fig:iid_spintilt_dist}
\end{figure}

@@

\begin{figure}
    \script{plot_ind_spintilt.py}
        \includegraphics[width=0.45\textwidth]{figures/ind_spintilt.pdf}
        \caption{Caption.}
        \label{fig:ind_spintilt_dist}
\end{figure}

@@

\begin{figure}
    \script{plot_chieff.py}
    \includegraphics[width=0.45\textwidth]{figures/chi_eff.pdf}
    \caption{Caption.}
    \label{fig:chieff_dist}
\end{figure}

>>>>

\begin{figure*}[ht!]
    \script{mass_distribution_plot.py}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/mass_distribution_plot.pdf}
        \caption{The primary mass distribution inferred with the \textsc{MSpline} model (red), with 50 knots spaced lineary in $\log m_1$, from the 
        minimum observed value to 100\msun. The solid line shows the population predictive distribution (PPD) and the shaded region, 
        the 90\% credible interval. We show the inferred PPD from the \textsc{PowerlawSpline} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
        \label{fig:mass_distribution}
    \end{centering}
\end{figure*}

@@

\begin{figure}
    \script{plot_iid_spinmag.py}
    \includegraphics[width=0.45\textwidth]{figures/iid_spinmag.pdf}
    \caption{The spin magnitude distribution inferred with the \textsc{MSpline} model (red), with 16 knots spaced linearly from 0 to 1, and 
    assuming the components are IID. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
    We show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
    \label{fig:iid_spinmag_dist}
\end{figure}

@@

\begin{figure}
    \script{plot_ind_spinmag.py}
    \includegraphics[width=0.45\textwidth]{figures/ind_spinmag.pdf}
    \caption{The primary (orange) and secondary (olive) spin magnitude distributions inferred with the \textsc{MSpline} model, 
    with 16 knots spaced linearly from 0 to 1. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
    We show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
    \label{fig:ind_spinmag_dist}
\end{figure}

@@

\begin{figure}
    \script{plot_iid_spintilt.py}
    \includegraphics[width=0.45\textwidth]{figures/iid_spintilt.pdf}
    \caption{The spin orientation distribution inferred with the \textsc{MSpline} model (red), with 16 knots spaced linearly from -1 to 1, and 
    assuming the components are IID. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
    We show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
    \label{fig:iid_spintilt_dist}
\end{figure}

@@

\begin{figure}
    \script{plot_ind_spintilt.py}
        \includegraphics[width=0.45\textwidth]{figures/ind_spintilt.pdf}
        \caption{The primary (orange) and secondary (olive) spin orientation distributions inferred with the \textsc{MSpline} model, 
        with 16 knots spaced linearly from -1 to 1. The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. 
        We show the inferred PPD from the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
        \label{fig:ind_spintilt_dist}
\end{figure}

@@

\begin{figure}
    \script{plot_chieff.py}
    \includegraphics[width=0.45\textwidth]{figures/chi_eff.pdf}
    \caption{The effective spin distribution inferred with the \textsc{MSpline} model (red), with 24 knots spaced linearly from -1 to 1. 
    The solid line shows the population predictive distribution (PPD) and the shaded region, the 90\% credible interval. We show the inferred $\chi_\mathrm{eff}$ 
    PPD from the IID component spin \textsc{MSpline} model (green), the independent component spin \textsc{MSpline} model (purple), 
    and the \textsc{Default} (blue) model from \citet{o3b_astro_dist}, the LVK's GWTC-3 population analyses.}
    \label{fig:chieff_dist}
\end{figure}
